Bad forecast, good decision: predictive accuracy is not everything

### 2020-11-05 manuscript/manuscript.Rmd
re-title

---
title: "Bad forecast, good decision: what makes a model relevant for determining policy"
date: "`r Sys.Date()`"
author:
  - name: Carl Boettiger
    email: cboettig@berkeley.edu
    affiliation: ucb
address:
  - code: ucb
    address: "ESPM Department, University of California, 130 Mulford Hall Berkeley, CA 94720-3114, USA"
abstract: |
    With the rapid expansion of available data, it is frequently suggested that _forecasting performance_ is the ultimate test of a scientific model.  Yet the model that makes the most accurate forecasts is not always the model that yields the best decisions.  This is no accident of statistics, even formal criteria such as strictly proper scoring rules cannot determine the best model for decision-making because they do not consider the context of the decision process itself.  I illustrate this paradox using a classic example of ecological decision making in fisheries management.  This example also reveals how an understanding of the decision problem can both explain the poor management outcomes of model which produces the best forecast, and also see how to avoid making such a mistake.  As forecasting becomes an increasing attractive and viable possibility for assessing ecological models and applying them to real-world decisions, I hope this illustration serves as a reminder that modeling can not be done in a vacuum, but must reflect the context in which the model will be applied.
journal: TBD
layout: 3p
bibliography: refs.bib
csl: nature.csl
output: 
  rticles::elsevier_article:
    dev: cairo_pdf
    keep_tex: true
keywords: 
  - transients, 
  - optimal control, 
  - adaptive management, 
  - stochasticity, 
  - uncertainty, 
  - ecological management
preamble: |
  \journal{preprint}
  \usepackage{lineno}
  \linenumbers

>>>>

---
title: "Bad forecast, good decision: predictive accuracy is not everything"
date: "`r Sys.Date()`"
author:
  - name: Carl Boettiger
    email: cboettig@berkeley.edu
    affiliation: ucb
address:
  - code: ucb
    address: "ESPM Department, University of California, 130 Mulford Hall Berkeley, CA 94720-3114, USA"
abstract: |
    With the rapid expansion of available data, it is frequently suggested that _forecasting performance_ is the ultimate test of a scientific model.  Yet the model that makes the most accurate forecasts is not always the model that yields the best decisions.  This is no accident of statistics, even formal criteria such as strictly proper scoring rules cannot determine the best model for decision-making because they do not consider the context of the decision process itself.  I illustrate this paradox using a classic example of ecological decision making in fisheries management.  This example also reveals how an understanding of the decision problem can both explain the poor management outcomes of model which produces the best forecast, and also see how to avoid making such a mistake.  As forecasting becomes an increasing attractive and viable possibility for assessing ecological models and applying them to real-world decisions, I hope this illustration serves as a reminder that modeling can not be done in a vacuum, but must reflect the context in which the model will be applied.
journal: TBD
layout: 3p
bibliography: refs.bib
csl: nature.csl
output: 
  rticles::elsevier_article:
    dev: cairo_pdf
    keep_tex: true
keywords: 
  - transients, 
  - optimal control, 
  - adaptive management, 
  - stochasticity, 
  - uncertainty, 
  - ecological management
preamble: |
  \journal{preprint}
  \usepackage{lineno}
  \linenumbers
